---
title: "Predicting Retailer Revenue"
author: "Arvind Koul, Ethel Zhang, Johnny Chiu, Saurabh Tripathi, Varun Gupta, Yuqing Liu"
date: "1/21/2018"
output: html_document
---



# Outline

* Set up
* Exploratory Data Analysis
* Feature Engineer
* Model Building
* Model selection

---
### Set up
```{r, warning=FALSE, message=FALSE}
# Set working directory and source function
pwd = getwd()
source(paste(pwd,'/function.R',sep=''))

# Read Data
booktrain_path = paste(getwd(),'/../data/booktrain.csv',sep='')
booktrain = read.csv(booktrain_path)
orders_path = paste(getwd(),'/../data/orders.csv',sep='')
orders = read.csv(orders_path)

# Only keep the rows from orders that can be matched to booktrain, i.e., the rows with logtarg.
all= merge(orders, booktrain, by='id',all.x= TRUE)

# Create Train and Test Dataset
train_original = all %>% filter(!is.na(logtarg)) # note that train data contains only 8224 customer id instead of 8311, since there are 87 ids in booktrain that can not be matched to the records in orders.
train_original = data_manipulate(train_original)

test_original = all %>% filter(is.na(logtarg))
test_original = data_manipulate(test_original)

```


### Exploratory Data Analysis
```{r}
### check NA
colSums(is.na(train_original)) # do not have any NA

### check the distribution for categorical columns
ggplot(data=train_original, aes(x=category)) + geom_histogram(binwidth=1)

### check outlier for numerical columns
# > qty
#check_outlier(train_original, 'qty', 10) # I think all the outliers are correct but extreme value. Decide to keep it for now.
#check_outlier(train_original, 'price', 10) # I think all the outliers are correct but extreme value. Decide to keep it for now.

# > price
# there are 3.25% of rows with the value 0 in column 'price', and most of them are from category 99 (61%).
#View(train_original[train_original$price==0,]) 
table(train_original[train_original$price==0,]$category)/dim(train_original[train_original$price==0,])[1]

```



### Feature Engineering
```{r, warning=FALSE, message=FALSE}
train = feature_engineer(train_original)
test = feature_engineer(test_original, isTrain=FALSE)
```

Here are the list 

| Feature | Description |
|---------------------------------------------------- | ----------------------------------------------------|
| days_recent_purchase | days since last purchase  |
| days_first_purchase | days since first purchase |
| order_count | total number of orders |
| avg_qty | average quantity per order|
| avg_ord_value | average order price |
| slope | build a linear regression for each id using date as predictor and daily total quantity as response and use the slope as the trend |
| coe_va | Coefficient of variation using the qty over year. The value is calculated using the variance divide by mean|

### Model Building

** Fit a simple regression model for benchmark**
```{r}
fit_multiple = lm(logtarg~.-id, data = train)
summary(fit_multiple)
vif(fit_multiple)
```

** Stepwise Linear Regression**
```{r}
# **Backward**
fit_stepback <- stepAIC(fit_multiple,direction = c("backward"))
summary(fit_stepback) # Adjusted R-squared:  0.01663

# **Forward**
fit_zero <- lm(logtarg ~ 1, data = train)
fit_stepforw <- stepAIC(fit_zero,direction = c("forward"), scope=list(upper=fit_multiple,lower=fit_zero))
summary(fit_stepforw) # Adjusted R-squared:  0.007776
```

** Lasso Linear Regression**
```{r}
y=train$logtarg
x=model.matrix(logtarg~.-id,train)
param_lasso = my_cv_glmnet(y,x,1)$small.lambda.betas
param_lasso = param_lasso[param_lasso!=0]
lasso_feature = c('logtarg','days_recent_purchase', 'days_first_purchase', 'order_count', 'avg_qty','coe_va')
fit_lasso = lm(logtarg~., data = train[lasso_feature])
summary(fit_lasso) #Adjusted R-squared:  0.01626
```


### Model selection
Choose the model according to Root Mean Square Error(RMSE)

In our final model, the significant features are 


| Feature | Description |
|---------------------------------------------------- | ----------------------------------------------------|
| days_recent_purchase | days since last purchase  |
| days_first_purchase | days since first purchase |
| order_count | total number of orders |
| avg_qty | average quantity per order|
| avg_ord_value | average order price |
| slope | build a linear regression for each id using date as predictor and daily total quantity as response and use the slope as the trend |
| coe_va | Coefficient of variation using the qty over year. The value is calculated using the variance divide by mean|



### Make prediction
```{r}
predict_reg = predict(fit_multiple, newdata=test)
```

### Generating submitting file
```{r}
test$logtarg = predict_reg
file_version1 = test %>% dplyr::select(id, logtarg)
file_version1$logtarg = ifelse(file_version1$logtarg<0, 0, file_version1$logtarg)
colnames(file_version1) = c('id','yhat')
# write.csv(file_version1, file=paste('./submission/model_',format(Sys.time(), "%b%d_%H%M%S"),'.csv',sep=''),row.names = FALSE)
```





##### > Linear Regression with custom chosen variables
chosen_feature = c('days_first_purchase', 'order_count', 'avg_qty',
                    'slope' ,'coe_va', 'logtarg')#'avg_qty', 'days_recent_purchase', 
fit_custom = lm(logtarg~., data = train[chosen_feature]) 
summary(fit_custom)

cv.lm(data=train[chosen_feature], m=10, form.lm=fit_custom) # ms 0.375
